---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/packettotal.svg?branch=master)](https://travis-ci.org/hrbrmstr/packettotal) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/packettotal/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/packettotal)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/packettotal)](https://cran.r-project.org/package=packettotal)

# packettotal

Lookup and Analyze Packet Capture ('PCAP') Files

## Description

'PacketTotal' (<https://packettotal.com/>) is an engine for analyzing, 
categorizing, and sharing packet capture ('PCAP') files. The tool was built 
with the information security community in mind and has applications in malware 
analysis and network forensics. Methods are provided to query search for and 
analyze packet capture files.

## What's Inside The Tin

The following functions are implemented:

- `packettotal_api_key`:	Get or set PACKETTOTAL_API_KEY value
- `pt_deep_search`/`pt_get_search_results`:	Create a new deep search task. Search for a term or with a Lucene query.
- `pt_detail`:	Get a detailed report of PCAP traffic, carved files, signatures, and top-talkers.
- `pt_download`:	Download a PCAP analysis archive. The result is a zip archive containing the PCAP itself, CSVs representing various analysis results, and all carved files.
- `pt_info`:	Get high-level information about a specific PCAP file.
- `pt_random`:	Get high-level information about a random PCAP file.
- `pt_search`:	Search with term or with a valid Lucene query.
- `pt_similar`:	Get a similarity graph relative to the current PCAP file.
- `pt_usage`:	Retrive usage and subscription plan information.

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/packettotal.git")
# or
devtools::install_github("hrbrmstr/packettotal")
```

## Usage

```{r lib-ex}
library(packettotal)

# current version
packageVersion("packettotal")

```

```{r random}
str(pt_random(), 2)
```

```{r search}
str(pt_search("evil.com"), 2)
```

```{r deep-search}
(res <- pt_deep_search("botnet OR malware"))

str(pt_get_search_results(res), 2)
```

```{r info}
str(pt_info("d210f4dbea97949f694e849507951881"), 2)
```

```{r detail}
str(pt_detail("d210f4dbea97949f694e849507951881"), 2)
```

```{r similar}
str(pt_similar("536cf06ca83704844d789f56caf22ee6"), 2)
```

## packettotal Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
